Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-06 methodology.tex
edit in Section 3
pass on our random experiment selection process

%Table \ref{tab:apps-detail} summarizes the details of each application. It shows the number of MPI ranks, the average data transfer amount of each rank and the total data transfer amount for each application.

>>>>

As a significant portion of our experiments rely on nondeterministic behavior (random application allocation), we ran each configuration a total of 50 times with differing random seeds. We then chose a representative execution for presentation based on the median performance of the AMG application trace. While there is variation in repeated runs of the following experiments, the resulting trends and observations are representative of the full suite of experimentation.
